MS_CNuptake.Rmd

### 2022-10-31 MS_CNuptake.Rmd
update

b1 <- as.ggplot(~barplot(vif_bp, main = "VIF of Forest BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C:N", "ln age", "ln vpd")))
b2 <- as.ggplot(~barplot(vif_anpp_tnpp, main = "VIF of Forest ABP/BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C:N", "ln age", "ln vpd")))
b3 <- as.ggplot(~barplot(vif_anpp_leafnpp, main = "VIF of Forest leaf-BP/ABP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln PPFD", "ln soil C:N", "ln age", "ln vpd")))
b4 <- as.ggplot(~barplot(vif_bp_grass, main = "VIF of Grassland BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "ln PPFD", "ln vpd", "ln soil C:N", "fAPAR")))
plot_grid(b1,b2,b3,b4,
          labels = c('(a)','(b)','(c)','(d)'),
          ncol=2,label_x = 0.9,label_y=0.92)+white
ggsave(paste("./output/figs4.jpg",sep=""),width = 10, height = 13)
```

@@

gg <- plot_map3(na.omit(PPFD[,c("lon","lat","PPFD")]),varnam = "PPFD",latmin = -65, latmax = 85,combine=FALSE,breaks = seq(100,800,100))
d7 <- gg$ggmap +labs(title = "PPFD")+theme_grey(base_size = 15)+ white;d8 <- gg$gglegend + labs(title =~paste(mu, "mol m"^-2,"s"^-1))+ white

@@

final1 <- ggplot() +xlim(8,30)+geom_line(data = subset(fits_tg,plt=="Measurement"), aes(Tg_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_tg, aes(Tg_a, visregFit, group=plt, color=plt),size=1) +theme_classic()+theme(text = element_text(size=20),legend.position="none")+  geom_ribbon(data = bp1a$fit,aes(Tg_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+labs(y = ~paste(BP, " (gC m"^-2,"yr"^-1,")"))+xlab("Tg (°C)")
final2 <- ggplot()+xlim(5.5,6.3)+geom_line(data = subset(fits_PPFD,plt=="Measurement"), aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")+geom_ribbon(data = bp1b$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+ scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab(~paste("ln PPFD (", mu, "mol m"^-2,"s"^-1, ")"))
final3 <- ggplot()+xlim(-0.8,1) +geom_line(data = subset(fits_vpd,plt=="Measurement"), aes(vpd_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_vpd, aes(vpd_a, visregFit, group=plt, color=plt),size=1) + ylab(" ") +theme_classic()+theme(text = element_text(size=20),legend.position="none")+ geom_ribbon(data = bp1c$fit,aes(vpd_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab("ln D (kPa)")

@@

final1c <- ggplot()+xlim(5.5,6.3) +geom_line(data = subset(fits_ppfd,plt=="Measurement"),aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_ppfd, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + 
  geom_ribbon(data=nn1c$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  xlab(~paste("ln PPFD (", mu, "mol m"^-2,"s"^-1, ")")) + ylab(" ")+
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+
  scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

@@

final1_nue8 <- ggplot()+xlim(5.5,6.3) +geom_line(data = nue8c$fit, aes(PPFD_a, visregFit),size=4) +
  geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) +
  xlab(~paste("ln PPFD (", mu, "mol m"^-2,"s"^-1, ")")) + ylab(" ")+
  geom_ribbon(data=nue8c$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

@@

@@

a7 <- ~{
  p1a <- visreg(anpp_tnpp_model,"PPFD_a",type="contrast")
  plot(p1a,ylab="logit ABP/BP",xlab="ln PPFD",line=list(col="white",lwd=0.01,lty=9), band=FALSE,
       cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)}

>>>>

b1 <- as.ggplot(~barplot(vif_bp, main = "VIF of Forest BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln gPPFD", "ln soil C:N", "ln age", "ln vpd")))
b2 <- as.ggplot(~barplot(vif_anpp_tnpp, main = "VIF of Forest ABP/BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln gPPFD", "ln soil C:N", "ln age", "ln vpd")))
b3 <- as.ggplot(~barplot(vif_anpp_leafnpp, main = "VIF of Forest leaf-BP/ABP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "fAPAR", "ln gPPFD", "ln soil C:N", "ln age", "ln vpd")))
b4 <- as.ggplot(~barplot(vif_bp_grass, main = "VIF of Grassland BP model", horiz = TRUE, col = "steelblue",
                         names.arg = c("Tg", "ln gPPFD", "ln vpd", "ln soil C:N", "fAPAR")))
plot_grid(b1,b2,b3,b4,
          labels = c('(a)','(b)','(c)','(d)'),
          ncol=2,label_x = 0.9,label_y=0.92)+white
ggsave(paste("./output/figs4.jpg",sep=""),width = 10, height = 13)
```

@@

gg <- plot_map3(na.omit(PPFD[,c("lon","lat","PPFD")]),varnam = "PPFD",latmin = -65, latmax = 85,combine=FALSE,breaks = seq(100,800,100))
d7 <- gg$ggmap +labs(title = "gPPFD")+theme_grey(base_size = 15)+ white;d8 <- gg$gglegend + labs(title =~paste(mu, "mol m"^-2,"s"^-1))+ white

@@

final1 <- ggplot() +xlim(8,30)+geom_line(data = subset(fits_tg,plt=="Measurement"), aes(Tg_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_tg, aes(Tg_a, visregFit, group=plt, color=plt),size=1) +theme_classic()+theme(text = element_text(size=20),legend.position="none")+  geom_ribbon(data = bp1a$fit,aes(Tg_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+labs(y = ~paste(BP, " (gC m"^-2,"yr"^-1,")"))+xlab("Tg (°C)")
final2 <- ggplot()+xlim(5.5,6.3)+geom_line(data = subset(fits_PPFD,plt=="Measurement"), aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")+geom_ribbon(data = bp1b$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+ scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab(~paste("ln gPPFD (", mu, "mol m"^-2,"s"^-1, ")"))
final3 <- ggplot()+xlim(-0.8,1) +geom_line(data = subset(fits_vpd,plt=="Measurement"), aes(vpd_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_vpd, aes(vpd_a, visregFit, group=plt, color=plt),size=1) + ylab(" ") +theme_classic()+theme(text = element_text(size=20),legend.position="none")+ geom_ribbon(data = bp1c$fit,aes(vpd_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab("ln D (kPa)")

@@

final1c <- ggplot()+xlim(5.5,6.3) +geom_line(data = subset(fits_ppfd,plt=="Measurement"),aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_ppfd, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + 
  geom_ribbon(data=nn1c$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  xlab(~paste("ln gPPFD (", mu, "mol m"^-2,"s"^-1, ")")) + ylab(" ")+
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+
  scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

@@

final1_nue8 <- ggplot()+xlim(5.5,6.3) +geom_line(data = nue8c$fit, aes(PPFD_a, visregFit),size=4) +
  geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) +
  xlab(~paste("ln gPPFD (", mu, "mol m"^-2,"s"^-1, ")")) + ylab(" ")+
  geom_ribbon(data=nue8c$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

@@

a2 <- ~{
  p1a <- visreg(bp_model,"PPFD_a",type="contrast")
  plot(p1a,ylab="Forest BP",xlab="ln gPPFD",
       cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)}

@@

a7 <- ~{
  p1a <- visreg(anpp_tnpp_model,"PPFD_a",type="contrast")
  plot(p1a,ylab="logit ABP/BP",xlab="ln gPPFD",line=list(col="white",lwd=0.01,lty=9), band=FALSE,
       cex.lab=1.5, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)}
